### 2020-12-20 paper/localpsf.tex
fixed infinite dimensional regularity issues

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to the Poisson problem
			\begin{equation}
			\label{eq:psi_eq}
			\Delta \psi_i = \delta_{x_i}, \quad \text{in }\Omega,
			\end{equation}
			with Neumann zero boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$.

@@

\begin{lem}[Preparation for Theorem \ref{thm:wi_alg_is_correct}]
	\label{lem:psi_delta_eval}
	We have
	\begin{equation}
	\label{eq:inline_wi_lemma}
	\left(\psi_j, \Delta h\right)_{L^2(\Omega)} = h(x_j) - \avg(h)
	\end{equation}
	for all $h\in H^2_N(\Omega)$, where
	\begin{equation*}
		\avg(h) :=	 \frac{1}{|\Omega|} \int_\Omega h ~dx.
	\end{equation*}
\end{lem}

\begin{proof}
	This is a standard result that follows from integration by parts and the definition of $\psi$ in \eqref{eq:psi_eq}.
\end{proof}

>>>>

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to the Poisson problem
			\begin{equation}
			\label{eq:psi_eq}
			\Delta \psi_i = \delta_{x_i} - C/|\Omega|, \quad \text{in }\Omega,
			\end{equation}
			with Neumann zero boundary conditions, $\nu \cdot \nabla \psi_i = 0$ on $\partial \Omega$, and the average value zero condition, $\int_\Omega \psi_i(x) dx = 0$. Recall $\delta_{x_i}$ is a point source (delta distribution) centered at $x_i$, $C$ is the constant function $C(x)=1$, and $|\Omega|$ is the Lebesgue measure of $\Omega$.

@@

\begin{lem}[Preparation for Theorem \ref{thm:wi_alg_is_correct}]
	\label{lem:psi_delta_eval}
	We have
	\begin{equation}
	\label{eq:inline_wi_lemma}
	h(x_j) = \left(\psi_j, \Delta h\right)_{L^2(\Omega)} + \avg(h)
	\end{equation}
	for all $h\in H^2_N(\Omega)$, where
	\begin{equation*}
		\avg(h) :=	 \frac{1}{|\Omega|} \int_\Omega h ~dx,
	\end{equation*}
	and $|\Omega| = \int_\Omega 1 ~dx$ is the Lebesgue measure of $\Omega$.
\end{lem}

\begin{proof}
	The result follows from multiplying \eqref{eq:psi_eq} by $h$, integrating both sides of the equation over $\Omega$, performing integration by parts to move derivatives from $\psi_j$ onto $h$, and using the Neumann zero boundary conditions for $\psi_j$ and $h$ to eliminate boundary integral terms.
%	
%	The standard weak form for $\psi_j$ in \eqref{eq:psi_eq} is given by the following saddle point system for $\psi_j \in H^1(\Omega)$ and $\rho \in \mathbb{R}$:
%	\begin{alignat}{5}
%		-\int_\Omega \nabla \psi_j \cdot \nabla h ~dx &~+~& \rho \int_\Omega h ~dx &~=~ h(x_j) &\quad \forall h \in H^1(\Omega) \label{eq:lem_delta_eval_feq} \\
%		\int_\Omega \psi_j ~dx & & &~=~ 0. & \nonumber
%	\end{alignat}
%	This follows from integration by parts, using the Neumann zero boundary conditions for $\psi_j$, and enforcing the average value zero constraint for $\psi_j$ with the Lagrange multiplier $\rho$. If $h$ is the constant function $h(x)=1$, the first equation becomes
%	\begin{equation*}
%		\rho \int_\Omega 1 ~ dx = 1,
%	\end{equation*}
%	which implies $\rho = \frac{1}{|\Omega|}$. Now suppose that $h\in H^2_N(\Omega)$. Of course, we still have $h\in H^1(\Omega)$ as well, so equation \eqref{eq:lem_delta_eval_feq} still holds. But now $h$ has additional regularity, which allows us to use integration by parts on the first term in \eqref{eq:lem_delta_eval_feq} to bring all of the derivatives onto $h$. Furthermore, $h$ has Neumann zero boundary conditions, so the boundary term that arises during integration by parts is zero. Performing this integration by parts, and substituting in the value for $\rho$, yields
%	\begin{equation*}
%		\int_\Omega \psi_j \Delta h ~dx + \frac{1}{|\Omega|} \int_\Omega h ~dx = h(x_j),
%	\end{equation*}
%	which is the desired result.
\end{proof}
